### 2014-10-27 core-lang.tex
Renamed Comm to EffVis

Rule $\rulelabel{Comm}$ captures inter-replica communication. The
basic guarantee provided by the store is causal visibility. That is,
an effect ($\eff$) is made visible at a replica $r$ only after all
the effects that causally precede $\eff$ are made visible at $r$.
Observe that this condition is applicable even for the effects that
originate at replica $r$. 
% It is helpful to think of effects being
% stored in a \emph{write buffer} until causal consistency condition is
% met, at which point they can be merged with the local state
% ($\Theta(r)$). 
It is important to note that that enforcing causal visibility does not
require any inter-replica coordination.

>>>>

Basic gurantee provided by the store is causal visibility, which is
captured by the rule $\rulelabel{EffVis}$ as a condition for an effect
to be visible at a replica. The rule makes an effect ($\eff$) visible
at a replica $r$ only after all the effects that causally precede
$\eff$ are made visible at $r$. 
% Observe that this condition is
% applicable even for the effects that originate at replica $r$. 
% It is helpful to think of effects being
% stored in a \emph{write buffer} until causal consistency condition is
% met, at which point they can be merged with the local state
% ($\Theta(r)$). 
It is important to note that that enforcing causal visibility does not
require any inter-replica coordination. Any eventually consistent
store can provide causal visibility while being highly available.
Therefore, we do not lose any generality by assuming that the store
provides causal visiblity.
